Marzuki Nooranas

### 2023-10-20 index.qmd
Update

@@

Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities. Here's a little snippet!

```{=html}
<style>
.tiktok-container {
  display: flex;
  flex-wrap: wrap;
  justify-content: center;
}

.tiktok-embed {
  max-width: 100%;
  flex: 1 1 300px;
}

@@

<p>overland travel for the vibesss. what a way to end 2022 phewww</p>

>>>>

## My overland journey from Singapore to Vietnam!

@@

Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities. Here's a little snippet -

```{=html}
<style>
body, html {
  margin: 0;
  padding: 0;
  overflow-x: hidden; 
}

.tiktok-container {
  display: flex;
  flex-wrap: wrap;
  justify-content: center;
  width: 105%; 
}

.tiktok-embed {
  box-sizing: border-box;
  max-width: 100%;
  flex: 1 1 300px;
  margin: 0 auto; 
}

@@

<p>overland travel for the vibesss</p>
